First Measurements of the D(e,e'p)n Cross Section at \\ Very High Recoil Momenta and Large Q^{2}

### 2020-01-07 MY_PUBLICATIONS/PRL/draft_v3/body.tex
updated

%:::::Rather than saying sensitivity to different NN potentials, say explicitly: "Up to 300 MeV/c, all models use a similar long-range part of the NN potential. Above 300 MeV/c, corresponding to the medium and short
% range parts of the NN potential, The Paris/AV18 PWIA agree, whereas the CD-Bonn PWIA is different, which indicates the NN potentials in the medium to short range parts greatly differe between the CD-Bonn and Paris/AV18.
%no model describes the data over the entire range--the data has a different shape than any of the models."

\indent Figure \ref{fig:fig1} shows the extracted experimental and theoretical reduced cross sections as a function of neutron recoil momentum $p_{r}$ for three angular settings at $Q^{2}=4.5\pm0.5$
(GeV/c)$^{2}$. The results from the previous Hall A experiment\cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$ are plotted as well (cyan). The data is compared to theoretical reduced
cross sections using the charge-dependent Bonn (CD-Bonn)\cite{PhysRevC.63.024001}, Argonne $v_{18}$ (AV18)\cite{PhysRevC.51.38} and Paris\cite{PhysRevC.21.861} NN-potentials. The theoretical calculations
for the CD-Bonn (magenta) and AV18 (green) potentials were performed by M. Sargsian\cite{PhysRevC.82.014612} and those for the Paris (blue) potential were done by J.M. Laget\cite{LAGET2005}. \\
\indent For the recoil angles shown in Fig. \hyperref[fig:fig1]{1(a)-(c)}, all models agree and the cross sections are dominated by the PWIA up to $p_{r}\sim$300 MeV/c, which corresponds to the long-range part
of the NN-potential which is well understood. Beyond $p_{r}\sim$300 MeV/c, at recoil angles $\theta_{nq}=35^{o}$ and $45^{o}$ [Figs. \hyperref[fig:fig1]{1(a), 1(b)}], the Paris and AV18 model cross sections are dominated by
the PWIA and are within good agreement up $p_{r}\sim750$ MeV/c, whereas the CD-Bonn calculation exhibits a different behaviour which indicates a larger sensitivity on the momentum distribution to the different NN-potentials
at higher missing momenta. At recoil angle $\theta_{nq}=75^{o}$ [Fig. \hyperref[fig:fig1]{1(c)}], FSIs become dominant at $p_{r}>300$MeV/c and exhibit a similar behaviour among all models which obscures any possibility
of extracting the momentum distributions at these angles. \\

>>>>

%:::::Rather than saying sensitivity to different NN potentials, say explicitly: "Up to 300 MeV/c, all models use a similar long-range part of the NN potential. Above 300 MeV/c,
%corresponding to the medium and short range parts of the NN potential, The Paris/AV18 PWIA agree, whereas the CD-Bonn PWIA is different, which indicates the NN potentials in
%the medium to short range parts greatly differe between the CD-Bonn and Paris/AV18. No model describes the data over the entire range--the data has a different shape than any of the models."

\indent Figure \ref{fig:fig1} shows the extracted experimental and theoretical reduced cross sections as a function of neutron recoil momentum $p_{r}$ for three angular settings at $Q^{2}=4.5\pm0.5$
(GeV/c)$^{2}$. The results from the previous Hall A experiment\cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$ are plotted as well (cyan). The data is compared to theoretical reduced
cross sections using the charge-dependent Bonn (CD-Bonn)\cite{PhysRevC.63.024001}, Argonne $v_{18}$ (AV18)\cite{PhysRevC.51.38} and Paris\cite{PhysRevC.21.861} NN-potentials. The theoretical calculations
for the CD-Bonn (magenta) and AV18 (green) potentials were performed by M. Sargsian\cite{PhysRevC.82.014612} and those for the Paris (blue) potential were done by J.M. Laget\cite{LAGET2005}. \\

\indent For the recoil angles shown in Fig. \hyperref[fig:fig1]{1(a)-(c)}, at recoil momenta up to $p_{r}\sim$300 MeV/c the cross sections are dominated by the PWIA and within agreement between all models.
The agreement at $p_{r}<300$ MeV/c can be understood from the fact that this region corresponds to the long-range part of the NN potential where the One Pion Exchange Potential (OPEP) is well known and commonly
used by high-quality potentials. Beyond $p_{r}\sim$300 MeV/c at $\theta_{nq}=35^{o}$ and $45^{o}$ [Figs. \hyperref[fig:fig1]{1(a), 1(b)}], the Paris and
AV18 models significantly differs from the CD-Bonn. The Paris/AV18 are dominated by the PWIA and within good agreement of each other up $p_{r}\sim750$ MeV/c, while the CD-Bonn exhibits a completely different
behaviour where the cross sections are smaller and dominated by the PWIA up to $p_{r}\sim800$ MeV/c for $theta_{nq}=35^{o}$\hyperref[fig:fig1]{1(a)}] and $p_{r}\sim580$ MeV/c for $\theta_{nq}=45^{o}$\hyperref[fig:fig1]{1(a)}].\\
The difference between the CD-Bonn and Paris/AV18
